Age-related changes in plant growth and traits

### 2015-09-03 RA_figs.rmd
figures for lab meeting

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)
results$yvar <- "growth_inv"
results$xvar <- "total_weight_0"
results$data <- "SummaryInd"
results$model <- "log10(yvar)~log10(xvar)"
saved_results <- as.data.frame(results)
results[1:6]

@@

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)
results$yvar <- "growth_inv"
results$xvar <- "leaf_area_0"
results$data <- "SummaryInd"
results$model <- "log10(yvar)~log10(xvar)"
saved_results <- bind_rows(saved_results,results)
results

@@

@@

>>>>

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)
results$yvar <- "growth_inv"
results$xvar <- "total_weight_0"
results$data <- "SummaryInd"
results$model <- "log10(yvar)~log10(xvar)"
results[1:6]

@@

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)
results$yvar <- "growth_inv"
results$xvar <- "leaf_area_0"
results$data <- "SummaryInd"
results$model <- "log10(yvar)~log10(xvar)"
saved_results <- as.data.frame(results)
results[1:6]

@@

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)
results$yvar <- "total_inv"
results$xvar <- "leaf_area_0"
results$data <- "SummaryInd"
results$model <- "log10(yvar)~log10(xvar)"
saved_results <- bind_cols(saved_results[1:2],results[2])
names(saved_results) <- c("species","r1","r2")
results[1:6]

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "leaf_area"
xvar <- "leaf_area_0"

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)
results$yvar <- "total_inv"
results$xvar <- "leaf_area_0"
results$data <- "SummaryInd"
results$model <- "log10(yvar)~log10(xvar)"
saved_results <- bind_cols(saved_results[1:2],results[2])
names(saved_results) <- c("species","r1","r2")
results[1:6]

mtext("Leaf area at time 1", 2, outer=TRUE,cex=1.2)
mtext("Leaf area at time 0", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=6, fig.height=6}
# pdf("figs2/R2-improve.pdf", height=5, width=5)
# plot
par(mfcol=c(1,1), cex=1, omi=c(.2,.2,.01,.01), mai=c(.8,.8,.04,0.2)) 
plot(r1~r2,saved_results,col=col.spp(species),pch=16,cex=1.1,cex.axis=0.8,cex.lab=0.8,ylab="R2 for veg invest vs leaf area",xlab="R2 for total invest vs leaf area",xlim=c(0,1),ylim=c(0,1))
abline(0,1)
text(r1~r2,saved_results, labels=species, pos=c("4","3","4","3","2","2","2","2","3","2","2","2","2","3"), offset=.4, cex=0.7,col="black")
saved_results$max_RA <- c("0.6","0.9","0.2","0.7","0.9","0.4","0.3","0.4","0.85","0.4","0.4","0.4","0.5","0.3")
text(r1~r2,saved_results, labels=max_RA, pos=c("1","1","1","1","1","1","4","1","1","1","3","3","1","1"), offset=.4, cex=0.7,col="black")
# dev.off()
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
pdf("figs2/shoot_leaf_area_VS_repro_inv.pdf", height=11.69, width=8.27)
plot
par(mfrow=c(4,4), cex=1, omi=c(.6,.5,.1,.1), mai=c(.35,.4,.25,0.1)) 
#par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2))
yvar <- "shoot_leaf_area"
xvar <- "repro_inv"

data <- subset(SummaryInd,repro_inv>0)
data <- split(data, data$species)

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.1,cex.axis=0.8,cex.main=0.9,
                    main=spp,col=col.age(data[[spp]]$age))
}

mtext("Shoot leaf area", 2, outer=TRUE,cex=1.2,line=1.2)
mtext("Reproductive investment (mg)", 1, outer=TRUE,cex=1.2,line=1.2)
legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
dev.off()
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
pdf("figs2/leaf_area_increase_VS_repro_inv.pdf", height=11.69, width=8.27)
plot
par(mfrow=c(4,4), cex=1, omi=c(.6,.5,.1,.1), mai=c(.35,.4,.25,0.1)) 
#par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "growth_leaf_area_log"
xvar <- "repro_inv"

data <- subset(SummaryInd,repro_inv>0)
data <- split(data, data$species)

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="",cex=1.1,cex.axis=0.8,cex.main=0.9,
                    main=spp,col=col.age(data[[spp]]$age))
}

mtext("Leaf area increase (log-log)", 2, outer=TRUE,cex=1.2,line=1.2)
mtext("Reproductive investment (mg)", 1, outer=TRUE,cex=1.2,line=1.2)
legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
dev.off()
```
